A Convolutional Neural Network for Outsole Recognition\tnoteref{t1}

### 2019-05-01 paper/paper.Rnw
At least begin to brainstorm--sorry

\svp{In order to train a new head for the VGG16 model base, human-labeled images are necessary. The next section describes how these images were produced and used to fit our custom classifier. }

@@

\begin{table}
\centering

\setlength\tabcolsep{1mm}
\begin{tabular}{rccl}
     Bowtie & \raisebox{-.5\height}{\includegraphics[width=.3\textwidth]{class_examples/bowtie_examples.png}} &
     \raisebox{-.5\height}{\includegraphics[width=.3\textwidth]{class_examples/chevron_examples.png}} & Chevron \vspace{1mm}\\
     Circle & \raisebox{-.5\height}{\includegraphics[width=0.3\textwidth]{class_examples/circle_examples.png}} &
     \raisebox{-.5\height}{\includegraphics[width=0.3\textwidth]{class_examples/line_examples.png}} & Line  \vspace{1mm}\\
     Polygon & \raisebox{-.5\height}{\includegraphics[width=0.3\textwidth]{class_examples/polygon_examples.png}} &
     \raisebox{-.5\height}{\includegraphics[width=0.3\textwidth]{class_examples/quad_examples.png}} & Quad  \vspace{1mm}\\
     Star & \raisebox{-.5\height}{\includegraphics[width=0.3\textwidth]{class_examples/star_examples.png}} &
     \raisebox{-.5\height}{\includegraphics[width=0.3\textwidth]{class_examples/text_examples.png}} & Text  \vspace{1mm}\\
     Triangle & \raisebox{-.5\height}{\includegraphics[width=0.3\textwidth]{class_examples/triangle_examples.png}} &
      \raisebox{-.5\height}{\includegraphics[width=0.3\textwidth]{class_examples/other_examples.png}} & Other \\
\end{tabular}
\caption[Geometric elements used to classify tread patterns.]{A set of geometric elements used to classify tread patterns. Categories modified from \cite{grossVariabilitySignificanceClass2013}.}\label{tab:class-char-examples}
\end{table}

@@

>>>>

In order to train a new head for the VGG16 model base, human-labeled images are necessary. The next section describes how these images were produced and used to fit our custom classifier.

@@

\mt{\begin{itemize}
\item Goal: Scheme that is broad enough to classify most shoes and specific enough to identify meaningful similarity between visually similar shoes
\item Papers (Gross et all, 2013) suggested geometric features have discriminatory power
\item Multi-label: label all shapes in a region
\item Modified: e.g., polygon out of pentagon and hexagon
\item Refer to table
\end{itemize}}

From CC:
Class characteristics, as defined in Section 1.2, are characteristics which can be used to exclude shoes from a match at a crime scene, but cannot be used for individualized matching because they are shared by many shoes. A sufficiently well-defined set of features can separate shoes into make and model categories (Gross et al., 2013). Gross et al. (2013) define geometric features such as circle/oval, crepe, herringbone, hexagon, parallel lines, logo/lettering/numbering, perimeter lugs, star, and other. Working from these categories, a set of categories were assembled that is more suited to recognition by convolutional neural networks, as some of the definitions used in Gross et al. (2013) require spatial context which is not preserved during labeling (for example, lugs are required to be on the perimeter of the shoe). Table 2.1 shows three examples of each class.

% \begin{table}
% \centering
%
% \setlength\tabcolsep{1mm}
% \begin{tabular}{rccl}
%      Bowtie & \raisebox{-.5\height}{\includegraphics[width=.3\textwidth]{class_examples/bowtie_examples.png}} &
%      \raisebox{-.5\height}{\includegraphics[width=.3\textwidth]{class_examples/chevron_examples.png}} & Chevron \vspace{1mm}\\
%      Circle & \raisebox{-.5\height}{\includegraphics[width=0.3\textwidth]{class_examples/circle_examples.png}} &
%      \raisebox{-.5\height}{\includegraphics[width=0.3\textwidth]{class_examples/line_examples.png}} & Line  \vspace{1mm}\\
%      Polygon & \raisebox{-.5\height}{\includegraphics[width=0.3\textwidth]{class_examples/polygon_examples.png}} &
%      \raisebox{-.5\height}{\includegraphics[width=0.3\textwidth]{class_examples/quad_examples.png}} & Quad  \vspace{1mm}\\
%      Star & \raisebox{-.5\height}{\includegraphics[width=0.3\textwidth]{class_examples/star_examples.png}} &
%      \raisebox{-.5\height}{\includegraphics[width=0.3\textwidth]{class_examples/text_examples.png}} & Text  \vspace{1mm}\\
%      Triangle & \raisebox{-.5\height}{\includegraphics[width=0.3\textwidth]{class_examples/triangle_examples.png}} &
%       \raisebox{-.5\height}{\includegraphics[width=0.3\textwidth]{class_examples/other_examples.png}} & Other \\
% \end{tabular}
% \caption[Geometric elements used to classify tread patterns.]{A set of geometric elements used to classify tread patterns. Categories modified from \cite{grossVariabilitySignificanceClass2013}.}\label{tab:class-char-examples}
% \end{table}

@@

\mt{\begin{itemize}
\item Mention that they're high school and/or undergrad lackeys? (Jk, students)
\item Number of shoe images, number of labels
\item Bar chart?
\end{itemize}}

\begin{figure}[hbt]
\centering
  \includegraphics[width=.9\textwidth]{images/LabelMe2.png}
  \caption{An example of labeling images with LabelMe}
\end{figure}
